---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
library(ral)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ral

Data package containing [RAL classic colors](https://en.wikipedia.org/wiki/RAL_colour_standard), mainly used for varnish and powder coating.

## Example

`ral` is a `data.frame` that contains RAL number, color, name, german name and a description.
```{r}
head(ral)
```

`ral_colors` is a named vector that can be used to quickly retrieve a color from the RAL number.

e.g.

```{r}
ral_colors["RAL9010"]
```

```{r, color table, echo=FALSE}
show_col <- function (colors, labels=colors, borders = NULL) 
{
    n <- length(colors)
    ncol <- ceiling(sqrt(n))
    nrow <- ceiling(n/ncol)
    colors <- c(colors, rep(NA, nrow * ncol - length(colors)))
    labels <- c(labels, rep("", nrow * ncol - length(labels)))
    colors <- matrix(colors, ncol = ncol, byrow = TRUE)
    labels <- matrix(labels, ncol=ncol, byrow=TRUE)
    old <- par(pty = "s", mar = c(0, 0, 0, 0))
    on.exit(par(old))
    size <- max(dim(colors))
    plot(c(0, size), c(0, -size), type = "n", xlab = "", ylab = "", 
        axes = FALSE)
    rect(col(colors) - 1, -row(colors) + 1, col(colors), -row(colors), 
        col = colors, border = borders)
    if (!missing(labels)) {
      text(col(colors) - 0.5, -row(colors) + 0.5, labels, cex=0.6)
    }
}

show_col(ral$color, ral$RAL, border=F)

```


##  Install

Currently `ral` is not available from CRAN and can be installed with the following:

```R
devtools::install_github("edwindj/ral")
```
