---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
library(ral)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/ral)](https://cran.r-project.org/package=ral)
[![Travis-CI Build Status](https://travis-ci.org/edwindj/ral.svg?branch=master)](https://travis-ci.org/edwindj/ral)

# ral

Data package containing [RAL classic colors](https://en.wikipedia.org/wiki/RAL_colour_standard), mainly used for varnish and powder coating.

## Example

`ral` is a `data.frame` that contains RAL number, color, name, german name and a description.
```{r}
head(ral)
```

`ral_colors` is a named vector that can be used to quickly retrieve a color from the RAL number.

```{r}
ralcolors["RAL9010"]
```

Function `show_ralcolors` shows the color table with corresponding RAL number.
```{r, color table}
show_ralcolors()
```


##  Install

Currently `ral` is not available from CRAN and can be installed with the following:

```R
devtools::install_github("edwindj/ral")
```
